A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex

>>>>

The CN2 software used supports different algorithms for building either ordered
or unordered rule sets and with different error estimations: laplacian, naive,
information gain and modified entropy. We've tested each combination of
parameters and the overall results are presented in table \ref{tbl:results_cn2}.

\begin{table}
\begin{center}
\begin{tabular}{ | l | l | l | l | l |}
    \hline
    \textbf{Algorithm} & \textbf{Error estimate} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    Unordered & Laplacian & 13.3 & 15.2 & 3min29sec \\ \hline
    Unordered & Naive & - & - & - \\ \hline
    Ordered & Laplacian & 0 & 17.6 & 1min45sec \\ \hline
    Ordered & Naive & 0 & 19.9 & 12min21sec \\ \hline
\end{tabular}
\caption{Results for CN2.}
\label{tbl:results_cn2}
\end{center}
\end{table}
